---
title: "Using the K-means Clustering Analysis for A Unleveraged Portfolio"
---

# Clean Data
### Loading data
```{r}
setwd('/Users/PROJECT')
library('readxl')
Energy <- read_excel("Project_data1.xlsx", sheet = 1, col_names = T, col_types = NULL, na = "", skip = 0)
Materials <- read_excel("Project_data1.xlsx", sheet = 2, col_names = T, col_types = NULL, na = "", skip = 0)
Industrials <- read_excel("Project_data1.xlsx", sheet = 3, col_names = T, col_types = NULL, na = "", skip = 0)
ConsumerDiscretionary <- read_excel("Project_data1.xlsx", sheet = 4, col_names = T, col_types = NULL, na = "", skip = 0)
ConsumerStaples <- read_excel("Project_data1.xlsx", sheet = 5, col_names = T, col_types = NULL, na = "", skip = 0)
HealthCare <- read_excel("Project_data1.xlsx", sheet = 6, col_names = T, col_types = NULL, na = "", skip = 0)
Financials <- read_excel("Project_data1.xlsx", sheet = 7, col_names = T, col_types = NULL, na = "", skip = 0)
InformationTechnology <- read_excel("Project_data1.xlsx", sheet = 8, col_names = T, col_types = NULL, na = "", skip = 0)
CommunicationService <- read_excel("Project_data1.xlsx", sheet = 9, col_names = T, col_types = NULL, na = "", skip = 0)
Utilities <- read_excel("Project_data1.xlsx", sheet = 10, col_names = T, col_types = NULL, na = "", skip = 0)
RealEstate <- read_excel("Project_data1.xlsx", sheet = 11, col_names = T, col_types = NULL, na = "", skip = 0)
```

### Calculate PEG
```{r}
NPGrowth <- function(df){
  df$NPGrowth <- (df$NP_L - df$NP_F) / df$NP_F
  return(df)
}

PEG <- function(df){
  df$PEG <- df$PE_Rolling / df$NPGrowth
  return(df)
}

Energy <- PEG(NPGrowth(Energy))
Materials <- PEG(NPGrowth(Materials))
Industrials <- PEG(NPGrowth(Industrials))
ConsumerDiscretionary <- PEG(NPGrowth(ConsumerDiscretionary))
ConsumerStaples <- PEG(NPGrowth(ConsumerStaples))
HealthCare <- PEG(NPGrowth(HealthCare))
Financials <- PEG(NPGrowth(Financials))
InformationTechnology <- PEG(NPGrowth(InformationTechnology))
CommunicationService <- PEG(NPGrowth(CommunicationService))
Utilities <- PEG(NPGrowth(Utilities))
RealEstate <- PEG(NPGrowth(RealEstate))
```

### Calculate Sharpe Average
```{r}
SharpeAvg <- function(df){
  df <- mean(df$Sharpe)
  return(df)
}

EnergySharpe <- SharpeAvg(Energy)
MaterialsSharpe <- SharpeAvg(Materials)
IndustrialsSharpe <- SharpeAvg(Industrials)
ConsumerDiscretionarySharpe <- SharpeAvg(ConsumerDiscretionary)
ConsumerStaplesSharpe <- SharpeAvg(ConsumerStaples)
HealthCareSharpe <- SharpeAvg(HealthCare)
FinancialsSharpe <- SharpeAvg(Financials)
InformationTechnologySharpe <- SharpeAvg(InformationTechnology)
CommunicationServiceSharpe <- SharpeAvg(CommunicationService)
UtilitiesSharpe <- SharpeAvg(Utilities)
RealEstateSharpe <- SharpeAvg(RealEstate)
```

### Calculate SPGrowthAvg
```{r}
SPGrowthAvg <- function(df){
  df <- mean(df$SPGrowth)
  return(df)
}

EnergySPGrowth <- SPGrowthAvg(Energy)
MaterialsSPGrowth <- SPGrowthAvg(Materials)
IndustrialsSPGrowth <- SPGrowthAvg(Industrials)
ConsumerDiscretionarySPGrowth <- SPGrowthAvg(ConsumerDiscretionary)
ConsumerStaplesSPGrowth <- SPGrowthAvg(ConsumerStaples)
HealthCareSPGrowth <- SPGrowthAvg(HealthCare)
FinancialsSPGrowth <- SPGrowthAvg(Financials)
InformationTechnologySPGrowth <- SPGrowthAvg(InformationTechnology)
CommunicationServiceSPGrowth <- SPGrowthAvg(CommunicationService)
UtilitiesSPGrowth <- SPGrowthAvg(Utilities)
RealEstateSPGrowth <- SPGrowthAvg(RealEstate)
```

### Calculate PEG Average
```{r}
PEGAvg <- function(df){
  df1 <- df$PEG[!is.nan(df$PEG)]
  df2 <- df1[!is.infinite(df1)]
  df <- mean(df2,na.rm=TRUE)
  return(df)
}

EnergyPEG <- PEGAvg(Energy)
MaterialsPEG <- PEGAvg(Materials)
IndustrialsPEG <- PEGAvg(Industrials)
ConsumerDiscretionaryPEG <- PEGAvg(ConsumerDiscretionary)
ConsumerStaplesPEG <- PEGAvg(ConsumerStaples)
HealthCarePEG <- PEGAvg(HealthCare)
FinancialsPEG <- PEGAvg(Financials)
InformationTechnologyPEG <- PEGAvg(InformationTechnology)
CommunicationServicePEG <- PEGAvg(CommunicationService)
UtilitiesPEG <- PEGAvg(Utilities)
RealEstatePEG <- PEGAvg(RealEstate)
```

### Create SumIndustry Table
```{r}
Industry <- c('Energy', 'Materials', 'Industrials', 'ConsumerDiscretionary', 'ConsumerStaples', 'HealthCare',
              'Financials', 'InformationTechnology', 'CommunicationService', 'Utilities', 'RealEstate')

SharpeAvg <- c(EnergySharpe,
               MaterialsSharpe,
               IndustrialsSharpe,
               ConsumerDiscretionarySharpe,
               ConsumerStaplesSharpe,
               HealthCareSharpe,
               FinancialsSharpe,
               InformationTechnologySharpe,
               CommunicationServiceSharpe,
               UtilitiesSharpe,
               RealEstateSharpe)

SPGrowthAvg <- c(EnergySPGrowth,
                 MaterialsSPGrowth ,
                 IndustrialsSPGrowth,
                 ConsumerDiscretionarySPGrowth,
                 ConsumerStaplesSPGrowth,
                 HealthCareSPGrowth,
                 FinancialsSPGrowth ,
                 InformationTechnologySPGrowth,
                 CommunicationServiceSPGrowth,
                 UtilitiesSPGrowth,
                 RealEstateSPGrowth)

PEGAvg <- c(EnergyPEG,
            MaterialsPEG,
            IndustrialsPEG,
            ConsumerDiscretionaryPEG,
            ConsumerStaplesPEG,
            HealthCarePEG,
            FinancialsPEG,
            InformationTechnologyPEG,
            CommunicationServicePEG,
            UtilitiesPEG,
            RealEstatePEG)

SumIndustry <- data.frame(Industry = Industry, SharpeAvg = SharpeAvg, SPGrowthAvg = SPGrowthAvg, PEGAvg = PEGAvg)
```

# Correlation Analysis
### Create Table
```{r}
SP2009 <- function(df){
  df$Time <- as.character(df$Time)
  mean(df$SP[df$Time == '2009-12-31'])
}

SP2010 <- function(df){
  df$Time <- as.character(df$Time)
  mean(df$SP[df$Time == '2010-12-31'])
}

SP2011 <- function(df){
  df$Time <- as.character(df$Time)
  mean(df$SP[df$Time == '2011-12-31'])
}

SP2012 <- function(df){
  df$Time <- as.character(df$Time)
  mean(df$SP[df$Time == '2012-12-31'])
}

SP2013 <- function(df){
  df$Time <- as.character(df$Time)
  mean(df$SP[df$Time == '2013-12-31'])
}

SP2014 <- function(df){
  df$Time <- as.character(df$Time)
  mean(df$SP[df$Time == '2014-12-31'])
}

SP2009 <- function(df){
  df$Time <- as.character(df$Time)
  mean(df$SP[df$Time == '2009-12-31'])
}

SP2015 <- function(df){
  df$Time <- as.character(df$Time)
  mean(df$SP[df$Time == '2015-12-31'])
}

SP2016 <- function(df){
  df$Time <- as.character(df$Time)
  mean(df$SP[df$Time == '2016-12-31'])
}

SP2017 <- function(df){
  df$Time <- as.character(df$Time)
  mean(df$SP[df$Time == '2017-12-31'])
}

SP2018 <- function(df){
  df$Time <- as.character(df$Time)
  mean(df$SP[df$Time == '2018-12-31'])
}



SP2009Energy <- SP2009(Energy)
SP2010Energy <- SP2010(Energy)
SP2011Energy <- SP2011(Energy)
SP2012Energy <- SP2012(Energy)
SP2013Energy <- SP2013(Energy)
SP2014Energy <- SP2014(Energy)
SP2015Energy <- SP2015(Energy)
SP2016Energy <- SP2016(Energy)
SP2017Energy <- SP2017(Energy)
SP2018Energy <- SP2018(Energy)

SP2009Materials <- SP2009(Materials)
SP2010Materials <- SP2010(Materials)
SP2011Materials <- SP2011(Materials)
SP2012Materials <- SP2012(Materials)
SP2013Materials <- SP2013(Materials)
SP2014Materials <- SP2014(Materials)
SP2015Materials <- SP2015(Materials)
SP2016Materials <- SP2016(Materials)
SP2017Materials <- SP2017(Materials)
SP2018Materials <- SP2018(Materials)

SP2009Industrials <- SP2009(Industrials)
SP2010Industrials <- SP2010(Industrials)
SP2011Industrials <- SP2011(Industrials)
SP2012Industrials <- SP2012(Industrials)
SP2013Industrials <- SP2013(Industrials)
SP2014Industrials <- SP2014(Industrials)
SP2015Industrials <- SP2015(Industrials)
SP2016Industrials <- SP2016(Industrials)
SP2017Industrials <- SP2017(Industrials)
SP2018Industrials <- SP2018(Industrials)

SP2009ConsumerDiscretionary <- SP2009(ConsumerDiscretionary)
SP2010ConsumerDiscretionary <- SP2010(ConsumerDiscretionary)
SP2011ConsumerDiscretionary <- SP2011(ConsumerDiscretionary)
SP2012ConsumerDiscretionary <- SP2012(ConsumerDiscretionary)
SP2013ConsumerDiscretionary <- SP2013(ConsumerDiscretionary)
SP2014ConsumerDiscretionary <- SP2014(ConsumerDiscretionary)
SP2015ConsumerDiscretionary <- SP2015(ConsumerDiscretionary)
SP2016ConsumerDiscretionary <- SP2016(ConsumerDiscretionary)
SP2017ConsumerDiscretionary <- SP2017(ConsumerDiscretionary)
SP2018ConsumerDiscretionary <- SP2018(ConsumerDiscretionary)

SP2009ConsumerStaples <- SP2009(ConsumerStaples)
SP2010ConsumerStaples <- SP2010(ConsumerStaples)
SP2011ConsumerStaples <- SP2011(ConsumerStaples)
SP2012ConsumerStaples <- SP2012(ConsumerStaples)
SP2013ConsumerStaples <- SP2013(ConsumerStaples)
SP2014ConsumerStaples <- SP2014(ConsumerStaples)
SP2015ConsumerStaples <- SP2015(ConsumerStaples)
SP2016ConsumerStaples <- SP2016(ConsumerStaples)
SP2017ConsumerStaples <- SP2017(ConsumerStaples)
SP2018ConsumerStaples <- SP2018(ConsumerStaples)

SP2009HealthCare <- SP2009(HealthCare)
SP2010HealthCare <- SP2010(HealthCare)
SP2011HealthCare <- SP2011(HealthCare)
SP2012HealthCare <- SP2012(HealthCare)
SP2013HealthCare <- SP2013(HealthCare)
SP2014HealthCare <- SP2014(HealthCare)
SP2015HealthCare <- SP2015(HealthCare)
SP2016HealthCare <- SP2016(HealthCare)
SP2017HealthCare <- SP2017(HealthCare)
SP2018HealthCare <- SP2018(HealthCare)

SP2009Financials <- SP2009(Financials)
SP2010Financials <- SP2010(Financials)
SP2011Financials <- SP2011(Financials)
SP2012Financials <- SP2012(Financials)
SP2013Financials <- SP2013(Financials)
SP2014Financials <- SP2014(Financials)
SP2015Financials <- SP2015(Financials)
SP2016Financials <- SP2016(Financials)
SP2017Financials <- SP2017(Financials)
SP2018Financials <- SP2018(Financials)

SP2009InformationTechnology <- SP2009(InformationTechnology)
SP2010InformationTechnology <- SP2010(InformationTechnology)
SP2011InformationTechnology <- SP2011(InformationTechnology)
SP2012InformationTechnology <- SP2012(InformationTechnology)
SP2013InformationTechnology <- SP2013(InformationTechnology)
SP2014InformationTechnology <- SP2014(InformationTechnology)
SP2015InformationTechnology <- SP2015(InformationTechnology)
SP2016InformationTechnology <- SP2016(InformationTechnology)
SP2017InformationTechnology <- SP2017(InformationTechnology)
SP2018InformationTechnology <- SP2018(InformationTechnology)

SP2009CommunicationService <- SP2009(CommunicationService)
SP2010CommunicationService <- SP2010(CommunicationService)
SP2011CommunicationService <- SP2011(CommunicationService)
SP2012CommunicationService <- SP2012(CommunicationService)
SP2013CommunicationService <- SP2013(CommunicationService)
SP2014CommunicationService <- SP2014(CommunicationService)
SP2015CommunicationService <- SP2015(CommunicationService)
SP2016CommunicationService <- SP2016(CommunicationService)
SP2017CommunicationService <- SP2017(CommunicationService)
SP2018CommunicationService <- SP2018(CommunicationService)

SP2009Utilities <- SP2009(Utilities)
SP2010Utilities <- SP2010(Utilities)
SP2011Utilities <- SP2011(Utilities)
SP2012Utilities <- SP2012(Utilities)
SP2013Utilities <- SP2013(Utilities)
SP2014Utilities <- SP2014(Utilities)
SP2015Utilities <- SP2015(Utilities)
SP2016Utilities <- SP2016(Utilities)
SP2017Utilities <- SP2017(Utilities)
SP2018Utilities <- SP2018(Utilities)

SP2009RealEstate <- SP2009(RealEstate)
SP2010RealEstate <- SP2010(RealEstate)
SP2011RealEstate <- SP2011(RealEstate)
SP2012RealEstate <- SP2012(RealEstate)
SP2013RealEstate <- SP2013(RealEstate)
SP2014RealEstate <- SP2014(RealEstate)
SP2015RealEstate <- SP2015(RealEstate)
SP2016RealEstate <- SP2016(RealEstate)
SP2017RealEstate <- SP2017(RealEstate)
SP2018RealEstate <- SP2018(RealEstate)

Year <- c('2009', '2010', '2011', '2012', '2013', '2014', '2015', '2016', '2017', '2018')

Energy <- c(SP2009Energy, SP2010Energy, SP2011Energy, SP2012Energy, SP2013Energy, 
            SP2014Energy, SP2015Energy, SP2016Energy, SP2017Energy, SP2018Energy)

Materials <- c(SP2009Materials, SP2010Materials, SP2011Materials, SP2012Materials, SP2013Materials,
               SP2014Materials, SP2015Materials, SP2016Materials, SP2017Materials, SP2018Materials)

Industrials <- c(SP2009Industrials, SP2010Industrials, SP2011Industrials, SP2012Industrials, SP2013Industrials, 
                 SP2014Industrials, SP2015Industrials, SP2016Industrials, SP2017Industrials, SP2018Industrials)

ConsumerDiscretionary <- c(SP2009ConsumerDiscretionary, SP2010ConsumerDiscretionary, SP2011ConsumerDiscretionary,
                           SP2012ConsumerDiscretionary, SP2013ConsumerDiscretionary, SP2014ConsumerDiscretionary, 
                           SP2015ConsumerDiscretionary, SP2016ConsumerDiscretionary, SP2017ConsumerDiscretionary, 
                           SP2018ConsumerDiscretionary)

ConsumerStaples <- c(SP2009ConsumerStaples, SP2010ConsumerStaples, SP2011ConsumerStaples, SP2012ConsumerStaples, 
                     SP2013ConsumerStaples, SP2014ConsumerStaples, SP2015ConsumerStaples, SP2016ConsumerStaples, 
                     SP2017ConsumerStaples, SP2018ConsumerStaples)

HealthCare <- c(SP2009HealthCare, SP2010HealthCare, SP2011HealthCare, SP2012HealthCare, SP2013HealthCare, 
                SP2014HealthCare, SP2015HealthCare, SP2016HealthCare, SP2017HealthCare, SP2018HealthCare)

Financials <- c(SP2009Financials, SP2010Financials, SP2011Financials, SP2012Financials, SP2013Financials, 
                SP2014Financials, SP2015Financials, SP2016Financials, SP2017Financials, SP2018Financials)

InformationTechnology <- c(SP2009InformationTechnology, SP2010InformationTechnology, SP2011InformationTechnology, SP2012InformationTechnology, 
                           SP2013InformationTechnology, SP2014InformationTechnology, SP2015InformationTechnology, SP2016InformationTechnology, 
                           SP2017InformationTechnology, SP2018InformationTechnology)

CommunicationService <- c(SP2009CommunicationService, SP2010CommunicationService, SP2011CommunicationService, SP2012CommunicationService, 
                          SP2013CommunicationService, SP2014CommunicationService, SP2015CommunicationService, SP2016CommunicationService, 
                          SP2017CommunicationService, SP2018CommunicationService)

Utilities <- c(SP2009Utilities, SP2010Utilities, SP2011Utilities, SP2012Utilities, SP2013Utilities, 
               SP2014Utilities, SP2015Utilities, SP2016Utilities, SP2017Utilities, SP2018Utilities)

RealEstate <- c(SP2009RealEstate, SP2010RealEstate, SP2011RealEstate, SP2012RealEstate, SP2013RealEstate, 
                SP2014RealEstate, SP2015RealEstate, SP2016RealEstate, SP2017RealEstate, SP2018RealEstate)

IndustryTable <- data.frame(Year = Year, Energy = Energy, Materials = Materials, Industrials = Industrials, 
                            ConsumerDiscretionary = ConsumerDiscretionary, ConsumerStaples = ConsumerStaples, 
                            HealthCare = HealthCare, Financials = Financials,
                            InformationTechnology = InformationTechnology, CommunicationService = CommunicationService, 
                            Utilities = Utilities, RealEstate = RealEstate)
```

### Convert to matrix
```{r}
IndustryMatrix <- matrix(nrow = 10, ncol = 11)
for (i in 1:11){
  IndustryMatrix[,i] <- IndustryTable[,i+1]
}
colnames(IndustryMatrix) <- c('Energy', 'Materials', 'Industrials', 'ConsumerDiscretionary', 'ConsumerStaples', 'HealthCare',
                              'Financials', 'InformationTechnology', 'CommunicationService', 'Utilities', 'RealEstate')
```

### Generate Correlation Chart1
```{r}
library(psych)
library(corrplot)
corr.test(IndustryMatrix, use = "complete", method = "pearson", adjust = "none")
res_cor <- cor(IndustryMatrix)
corrplot(corr = res_cor)
```

### Generate Correlation Chart2
```{r}
library(PerformanceAnalytics)
chart.Correlation(IndustryMatrix, method = "pearson")
```


# Clean Data
### Loading data
```{r}
setwd('/Users/jialantian/Desktop/FE 582/PROJECT')
library('readxl')
Financials <- read_excel("Project_data2.xlsx", sheet = 1, col_names = T, col_types = NULL, na = "", skip = 0)
ConsumerDiscretionary <- read_excel("Project_data2.xlsx", sheet = 1, col_names = T, col_types = NULL, na = "", skip = 0)
InformationTechnology <- read_excel("Project_data2.xlsx", sheet = 1, col_names = T, col_types = NULL, na = "", skip = 0)
Energy <- read_excel("Project_data2.xlsx", sheet = 1, col_names = T, col_types = NULL, na = "", skip = 0)
```

### Clean data
```{r}
SP <- function(df){
  df$Time <- as.character(df$Time)
  SP <- df$SP_C[df$Time == '2015-03-31']
}

V <- function(df){
  df$Time <- as.character(df$Time)
  V <- df$V_C[df$Time == '2015-03-31']
}

B <- function(df){
  df$Time <- as.character(df$Time)
  B <- df$B_C[df$Time == '2015-03-31']
}

EPS <- function(df){
  df$Time <- as.character(df$Time)
  EPS <- df$EPS_C[df$Time == '2015-03-31']
}

PE <- function(df){
  df$Time <- as.character(df$Time)
  PE <- df$PE_C[df$Time == '2015-03-31']
}

NAME <- function(df){
  df$Time <- as.character(df$Time)
  NAME <- df$StockName[df$Time == '2015-03-31']
}

EnergyNAME <- NAME(Energy)
FinancialsNAME <- NAME(Financials)
ConsumerDiscretionaryNAME <- NAME(ConsumerDiscretionary)
InformationTechnologyNAME <- NAME(InformationTechnology)

EnergySP <- SP(Energy)
FinancialsSP <- SP(Financials)
ConsumerDiscretionarySP <- SP(ConsumerDiscretionary)
InformationTechnologySP <- SP(InformationTechnology)

EnergyV <- V(Energy)
FinancialsV <- V(Financials)
ConsumerDiscretionaryV <- V(ConsumerDiscretionary)
InformationTechnologyV <- V(InformationTechnology)

EnergyB <- B(Energy)
FinancialsB <- B(Financials)
ConsumerDiscretionaryB <- B(ConsumerDiscretionary)
InformationTechnologyB <- B(InformationTechnology)

EnergyEPS <- EPS(Energy)
FinancialsEPS <- EPS(Financials)
ConsumerDiscretionaryEPS <- EPS(ConsumerDiscretionary)
InformationTechnologyEPS <- EPS(InformationTechnology)

EnergyPE <- PE(Energy)
FinancialsPE <- PE(Financials)
ConsumerDiscretionaryPE <- PE(ConsumerDiscretionary)
InformationTechnologyPE <- PE(InformationTechnology)
```

### Create table
```{r}
Stocks <- c(EnergyNAME, FinancialsNAME, ConsumerDiscretionaryNAME, InformationTechnologyNAME)
SPs <- c(EnergySP, FinancialsSP, ConsumerDiscretionarySP, InformationTechnologySP)
Vs <- c(EnergyV, FinancialsV, ConsumerDiscretionaryV, InformationTechnologyV)
Bs <- c(EnergyB, FinancialsB, ConsumerDiscretionaryB, InformationTechnologyB)
EPSs <- c(EnergyEPS, FinancialsEPS, ConsumerDiscretionaryEPS, InformationTechnologyEPS)
PEs <- c(EnergyPE, FinancialsPE, ConsumerDiscretionaryPE, InformationTechnologyPE)
SumTable <- data.frame(Stocks = Stocks, SPs = SPs, Vs = Vs, Bs = Bs, EPSs = EPSs, PEs = PEs)
```

### Clustering
```{r}
set.seed(00)
data_scale <- scale(SumTable[2:6])
data_dist <- dist(data_scale)
data_average <- hclust(data_dist,method='average')
kmeans(SumTable[2:6], 5)
```

### Plot Clustering Results
```{r}
library(ggfortify)
autoplot(kmeans(SumTable[2:6], 5), data = data_scale, label=TRUE, label.size=3, frame=TRUE)
```

# Determine Stocks
### First Stock
```{r}
ca.distance <- function(x){
  return((x[1] + 0.0087268953)^2 + (x[2] - 5.11569983)^2 + (x[3] - 0.5787793)^2 + (x[4] - 14.7131779)^2 + (x[5] + 0.009089698)^2)
}
result <- NULL
for (i in (1:2582)){
  result[i] <- ca.distance(SumTable[i,2:6])
}

location = 1
min.value=result[1]
for (i in 2:2582){
  if (as.numeric(result[i])<min.value){
    location=i
    min.value=result[i]
  }
}
location
min.value

SumTable[980,]
```

### Second Stock
```{r}
ca.distance <- function(x){
  return((x[1] - 0.0215762381)^2 + (x[2] - 0.12369282)^2 + (x[3] + 0.3681778)^2 + (x[4] - 1.2316371)^2 + (x[5] - 0.029389332)^2)
}
result <- NULL
for (i in (1:2582)){
  result[i] <- ca.distance(SumTable[i,2:6])
}

location = 1
min.value=result[1]
for (i in 2:2582){
  if (as.numeric(result[i])<min.value){
    location=i
    min.value=result[i]
  }
}
location
min.value

SumTable[1103,]
```


### Third Stock
```{r}
ca.distance <- function(x){
  return((x[1] + 0.0008119161)^2 + (x[2] - 0.06563434)^2 + (x[3] - 0.2846815)^2 + (x[4] + 0.2104281)^2 + (x[5] - 0.006860593)^2)
}
result <- NULL
for (i in (1:2582)){
  result[i] <- ca.distance(SumTable[i,2:6])
}

location = 1
min.value=result[1]
for (i in 2:2582){
  if (as.numeric(result[i])<min.value){
    location=i
    min.value=result[i]
  }
}
location
min.value

SumTable[1118,]
```

### Forth Stock
```{r}
ca.distance <- function(x){
  return((x[1] - 0.0559546923)^2 + (x[2] + 0.04004368)^2 + (x[3] + 188.0200428)^2 + (x[4] - 0.9454212)^2 + (x[5] - 0.023996164)^2)
}
result <- NULL
for (i in (1:2582)){
  result[i] <- ca.distance(SumTable[i,2:6])
}

location = 1
min.value=result[1]
for (i in 2:2582){
  if (as.numeric(result[i])<min.value){
    location=i
    min.value=result[i]
  }
}
location
min.value

SumTable[1180,]
```

### Fifth Stock
```{r}
ca.distance <- function(x){
  return((x[1])^2 + (x[2])^2 + (x[3])^2 + (x[4] + 112.0000000)^2 + (x[5])^2)
}
result <- NULL
for (i in (1:2582)){
  result[i] <- ca.distance(SumTable[i,2:6])
}

location = 1
min.value=result[1]
for (i in 2:2582){
  if (as.numeric(result[i])<min.value){
    location=i
    min.value=result[i]
  }
}
location
min.value

SumTable[623,]
```

### Create Variance and Mean Table
```{r}
Var1 <- var(Financials$SP_C[FinancialsNAME == 'Ready Capital Corp'])
Var2 <- var(Financials$SP_C[FinancialsNAME == 'S&T Bancorp Inc'])
Var3 <- var(Financials$SP_C[FinancialsNAME == 'Solar Senior Capital Ltd'])
Var4 <- var(Financials$SP_C[FinancialsNAME == '180 Degree Capital Corp'])
Var5 <- var(Financials$SP_C[FinancialsNAME == 'Investcorp Credit Management BDC Inc'])

Mean1 <- mean(Financials$SP_C[FinancialsNAME == 'Ready Capital Corp'])
Mean2 <- mean(Financials$SP_C[FinancialsNAME == 'S&T Bancorp Inc'])
Mean3 <- mean(Financials$SP_C[FinancialsNAME == 'Solar Senior Capital Ltd'])
Mean4 <- mean(Financials$SP_C[FinancialsNAME == '180 Degree Capital Corp'])
Mean5 <- mean(Financials$SP_C[FinancialsNAME == 'Investcorp Credit Management BDC Inc'])

Stocks <- c("Ready Capital Corp", "S&T Bancorp Inc", "Solar Senior Capital Ltd ", "180 Degree Capital Corp", "Investcorp Credit Management BDC Inc")
VAR <- c(Var1, Var2, Var3, Var4, Var5)
MEAN <- c(Mean1, Mean2, Mean3, Mean4, Mean5)

c <- data.frame(Stocks=Stocks, MEAN=MEAN, VAR=VAR)
c
```

### Create Proportion Table
```{r}
S11 <- c(1, 0.03, -0.23, 0.18, 0.13)
S22 <- c(0.03, 1, -0.11, -0.16,0.23)
S33 <- c(-0.23, -0.11, 1, -0.31, -0.15)
S44 <- c(0.18, -0.16, -0.31, 1, -0.09)
S55 <- c(0.13, 0.23, -0.15, -0.09, 1)
b <- data.frame(S11=S11, S22=S22, S33=S33, S44=S44, S55=S55)
b
```

### Calculate Weights
```{r}
for (i in 1:5){
  c[i,2] <- c[i,2]-0.01579/4
}
result.weight <- c(0,0,0,0,0)
result.sharpe <- 0
for (i in 1:10000){
  w5 <- runif(1,min=0,max=1)
  w2 <- runif(1,min=0,max=1-w5)
  w3 <- runif(1,min=0,max=1-w5-w2)
  w4 <- runif(1,min=0,max=1-w5-w2-w3)
  w1 <- runif(1,min=0,max=1-w5-w2-w3-w4)
  ex.return <- w1*c[1,2]+w2*c[2,2]+w3*c[3,2]+w4*c[4,2]+w5*c[5,2]
  ex.dev <- ((w1^2)*(c[1,3])^2 + (w2^2)*(c[2,3])^2 + (w3^2)*(c[3,3])^2 + (w4^2)*(c[4,3])^2 + (w5^2)*(c[5,3])^2 +
               w1*w2*c[1,3]*c[2,3]*b[1,2] + w1*w3*c[1,3]*c[3,3]*b[1,3] + w1*w4*c[1,3]*c[4,3]*b[1,4] + w1*w5*c[1,3]*c[5,3]*b[1,5] + w2*w3*c[2,3]*c[3,3]*b[2,3] + 
               w2*w4*c[2,3]*c[4,3]*b[2,4] + w2*w5*c[2,3]*c[5,3]*b[2,5] + w3*w4*c[3,3]*c[4,3]*b[3,4] + w3*w5*c[3,3]*c[5,3]*b[3,5] + w4*w5*c[4,3]*c[5,3]*b[4,5])^0.5
  sharpe <- ex.return/ex.dev
  if (sharpe > result.sharpe){
    result.sharpe=sharpe
    result.weight=c(w1,w2,w3,w4,w5)
  }
}
(ex.return+1)^4
ex.dev
result.sharpe
result.weight
```



